Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits

### 2022-10-06 04_paper/10_06_draft_newabstract.Rmd
Add files via upload

abstract: "[*old abstract*] Absent formal avenues of transparency, how do China's efforts at gaining international recognition and promoting good relations with aid recipients play out in Beijings foreign aid giving? We bring a novel perspective to this issue by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) meta-data of millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

@@

```{r aid-debt-country, fig.cap='Top 20 Chinese Aid Recipients (left) and Debt Recipients (right) on Average from 2002 to 2017.', out.width="100%",fig.show='hold'}
include_graphics(
  here('06_figures/aid_debt.jpg'))

```

@@

```{r compositions, fig.cap='The Aid-Debt Composition of the Top 20 Chinese Aid and Debt Recipients on Average from 2002 to 2017.', out.width="100%",fig.show='hold'}
include_graphics(
  here('06_figures/portfolio.jpg'))

```

>>>>

abstract: "Absent formal avenues of transparency, how do China’s foreign aid and debt allocation relate to public diplomacy and international recognition efforts? We bring a novel perspective to this issue by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. We also distinguish Beijing-as-donor and Beijing-as-lender. We propose that despite the lack of formal reporting, Beijing can pursue international recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid and debt giving. To test this expectation, we leverage (1) AidData’s Chinese development finance datasets and yearly counts of bilateral official diplomatic visits from China and (2) the meta-data of millions of English edition Xinhua news articles from 2000 to 2017 in the Cline Center for Advanced Social Research. We find that China pays more media attention to aid recipients but engages more in diplomatic visits with debtors. Aid recipient countries disproportionately get more media attention from Xinhua via news stories that report both the state of their economy and their developmental needs. Notably, Xinhua does not just promote China’s efforts but also gives a round picture of the countries’ economic conditions in justifying their legitimate need for aid. Our results dispel the myths of China as a ’rouge donor’ and Chinese ’debt-trap diplomacy.’ We suggest that much like traditional donors, China’s foreign aid presents a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics. Also, China is more likely to provide loans to diplomatically aligned countries."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```
\clearpage

@@

```{r aid-debt-country, fig.cap='Top 20 Chinese Aid Recipients (left) and Debt Recipients (right) on Average from 2002 to 2017.', out.width="100%",fig.show='hold'}
include_graphics(
  here('06_figures/aid_debt.jpg'))
```

@@

```{r compositions, fig.cap='The Aid-Debt Composition of the Top 20 Chinese Aid and Debt Recipients on Average from 2002 to 2017.', out.width="100%",fig.show='hold'}
include_graphics(
  here('06_figures/portfolio.jpg'))
```
